---
title: "Alcohol vs Seat choice"
author: "Sophia Castellon"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The average of alcohol consumption in ounces for those seated in the back is 8.5, which is higher then the average of those in the middle who's alcohol consumption was 3.33 ounces and the front had the least amount of alcohol consumption with 1.79 ounces. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
P value is .000116 which is lower than .05, so we reject the null hypothesis 

```{r}
plot(TukeyHSD(model1))
```

The tukey shows that the middle front has no difference where middle back and front have a difference. 

## Conclusions

We conclude that the alcohol consumption of those who are seated in the back were higher then those who sat in the middle or front. The numerical results show the average consumption of alcohol of those in the back was 8.5 where the middle was 3.3 and the front was 1.7. The P value is .000116 which is lower then .05 so we reject the null hypothesis as there is a difference in the alcohol consumption based on where you are seated. 

